Equation-of-state insensitive relations after GW170817

### 2019-02-24 paper/bin-love-after-gw170817.tex
add sentences about GWOSC and LI

The unconstrained set is then defined by drawing random samples in the spectral coefficients (within their allowed prior ranges), and then eliminating any EoS that either leads to a polytropic index $\Gamma$ outside the allowed range, breaks the causality restriction, or breaks the maximum mass restriction. The constrained set is defined in a similar way, with the addition of the restriction that the resulting EoS be inside the 90\% marginalized posterior distribution on the pressure-mass density plane derived from the GW170817 observation~\cite{LIGO:posterior,Carney:2018sdv}  (see Fig.~2 in~\cite{LIGO:posterior}). In both cases, each set consists of 100 members, with a subset of these shown in the left panel of Fig.~\ref{fig:eos}.\kc{wait, aren't you using the samples that Calr sent you directly? If yes we need to describe how they were computed and add the appropriate citations to code and data. But that's not what you are describing here}

@@

\section*{Acknowledgments}\label{acknowledgments}
K.Y. acknowledge networking support by the COST Action GWverse CA16104.
N.Y. acknowledges support from  NSF grant PHY-1759615 and NASA grants NNX16AB98G and 80NSSC17M0041.

>>>>

The unconstrained set is then defined by drawing random samples in the spectral coefficients within their allowed prior ranges, and then eliminating any EoS that either leads to a polytropic index $\Gamma$ outside the allowed range, breaks the causality restriction, or breaks the maximum mass restriction. 
To obtain the constrained set of EoSs we analyze the publicly available data for GW170817 from the Gravitational Wave Open Science Center~\cite{GWOSC,Vallisneri:2014vxa}. We use the publicly available software library {\tt LALInference}~\cite{Veitch:2014wba,lalinference_o2} to obtain samples from the EoS posterior. Our anaysis uses the same settings and prior choice as those of~\cite{LIGO:posterior,Carney:2018sdv}. 
In both cases, each set consists of 100 members, with a subset of these shown in the left panel of Fig.~\ref{fig:eos}.

%The constrained set is defined in a similar way, with the addition of the restriction that the resulting EoS be inside the 90\% marginalized posterior distribution on the pressure-mass density plane derived from the GW170817 observation~\cite{LIGO:posterior,Carney:2018sdv}  (see Fig.~2 in~\cite{LIGO:posterior}). In both cases, each set consists of 100 members, with a subset of these shown in the left panel of Fig.~\ref{fig:eos}.\kc{wait, aren't you using the samples that Calr sent you directly? If yes we need to describe how they were computed and add the appropriate citations to code and data. But that's not what you are describing here}

@@

\section*{Acknowledgments}\label{acknowledgments}
K.Y. acknowledge networking support by the COST Action GWverse CA16104.
N.Y. acknowledges support from  NSF grant PHY-1759615 and NASA grants NNX16AB98G and 80NSSC17M0041.
%
This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open Science Center (https://www.gw-openscience.org), a service of LIGO Laboratory, the LIGO Scientific Collaboration and the Virgo Collaboration. LIGO is funded by the U.S. National Science Foundation. Virgo is funded by the French Centre National de Recherche Scientifique (CNRS), the Italian Istituto Nazionale della Fisica Nucleare (INFN) and the Dutch Nikhef, with contributions by Polish and Hungarian institutes.
%
The authors are grateful for computational resources provided by the LIGO Laboratory and supported by National Science Foundation Grants PHY-0757058 and PHY-0823459.
